\newpage
\begin{thebibliography}{99}
  % \bibitem{mqm}
  %   \textit{Meccanica quantistica molecolare},
  %   Atkins Friedman,
  %   1983.

  \bibitem{S24}
    \textit{La densità della legge di Moore},
    Antonio Dini,
    Sole 24 ore,
    16 Aprile 2017.

  \bibitem{NAC}
    \textit{Notes on Adiabatic Quantum Computers},
    Boaz Tamir, Eliahu Cohen,
    2016.

  \bibitem{ACI}
    \textit{Architectural considerations in the design of a superconducting quantum annealing processor},
    P. I. Bunyk, E. Hoskinson, M. W. Johnson, E. Tolkacheva, F. Altomare, A. J. Berkley, R. Harris, J. P. Hilton, T. Lanting, J. Whittaker,
    2014.

  \bibitem{QAS}
    \textit{Quantum annealing with manufactured spins},
    M. W. Johnson, M. H. S. Amin, S. Gildert, T. Lanting, F. Hamze, N. Dickson, R. Harris, A. J. Berkley, J. Johansson, P. Bunyk, E. M. Chapple, C. Enderud, J. P. Hilton, K. Karimi, E. Ladizinsky, N. Ladizinsky, T. Oh, I. Perminov, C. Rich, M. C. Thom, E. Tolkacheva, C. J. S. Truncik, S. Uchaikin, J. Wang, B. Wilson, G. Rose,
    2011.

  % \bibitem{mcp}
  %   \textit{Programming with D-Wave: Map Coloring Problem},
  %   E. D. Dahl,
  %   2013.

  % \bibitem{jjq}
  %   \textit{Superconducting Qubits and the Physics of Josephson Junctions},
  %   John M. Martinis, Kevin Osborne,
  %   2004.


  \bibitem{QA}
    \textit{Colloquium: Quantum annealing and analog quantum computation},
    Arnab Das, Bikas K. Chakrabarti,
    5 Settembre 2008.

  \bibitem{MC}
    \textit{Introducing Monte Carlo Methods with R, Use R},
    C.P. Robert, G. Casella
    2010.

  \bibitem{ST}
    \textit{Simulated Annealing and Boltzmann Machines},
    E. Aarts, J. Korst e W. Michiels,
    1989.

  \bibitem{PIMC}
    \textit{Quantum annealing by the path-integral Monte Carlo method: The two-dimensional random Ising model},
    Roman Martonak, Giuseppe E. Santoro, Erio Tosatti,
    13 Settembre 2002.

  \bibitem{QVC}
    \textit{Quantum versus classical annealingof Ising spin glasses},
    Bettina Heim, Troels F. Rønnow, Sergei V. Isakov, Matthias Troyer,
    12 Marzo 2015.

  \bibitem{QS}
    \textit{Quantum supremacy, here we com},
    Barbara M. Terhal,
    23 Aprile 2018.

  \bibitem{MA}
    \textit{Realizing Majorana zero modes in superconductor-semiconductor heterostructures},
    M. Lutchyn, E. P. A. M. Bakkers, L. P. Kouwenhoven, P. Krogstrup,C. M. Marcus, Y. Oreg,
    24 Febbraio 2018.

  \bibitem{Q49}
    \textit{The Future of Quantum Computing is Counted in Qubits},
    Intel Website,
    2 Maggio 2018.

  \bibitem{DDQS}
    \textit{Defining and detecting quantum speedup},
    Troels F. Rønnow, Zhihui Wang, Joshua Job, Sergio Boixo, Sergei V. Isakov, David Wecker, John M. Martinis, Daniel A. Lidar, Matthias Troyer,
    25 Luglio 2014.

  \bibitem{EQA}
    \textit{Evidence for quantum annealing with more than
one hundred qubits},
    Sergio Boixo, Troels F. Rønnow, Sergei V. Isakov, ZhihuiWang, DavidWecker, Daniel A. Lidar, John M. Martinis and Matthias Troyer,
    28 Febbraio 2014.

  \bibitem{TSQA}
    \textit{Theory of Quantum Annealing of an Ising Spin Glass},
    Giuseppe E. Santoro, Roman Martonÿak, Erio Tosatti, Roberto Car,
    29 Marzo 2002.

  \bibitem{NCD}
    \textit{Nonuniversal Critical Dynamics in Monte Carlo Simulations},
    Robert H. Swendsen, Jian-Sheng Wang,
    19 Gennaio 1987.


\end{thebibliography}
